Multisequence algorithm for coarse-grained biomolecular simulations: application to protein fold switching

### 2017-06-02 Manuscript.tex
Modified computational efficiency section

As a way to assess sampling efficiency, we compare in Figure~4 the statistical error, $\sigE$, of the average energy $\left <E\right >$ for the 4 different sequences obtained using ST and MS, respectively. Since roughly the same number of sampled conformations were obtained for each s and $T$ combination, we can compare the statistical errors directly. Both MS and ST algorithms give the same small error at the highest $T$ studied which implies consistent result between them. It should be noted that the highest $T$ studied is well above the folding temperature for all the 4 sequences. Therefore, this consistent result is not particularly surprising since at high-T the free-energy landscape is relatively smooth. Hence, conformational space requires little or no difficulty to sample.

There is a sequence-dependent statistical trend observed in Figure 6. As temperature decreases, the statistical error from the MS algorithm becomes smaller than those from ST. Even at the lowest T studied, below the folding temperature of all 4 sequences, we notice that the MS algorithm is at least consistent and most times better than ST in its estimates except for N1. This departure from the dominant trend is most likely due to statistical flunctuations, in which case, does not have any considerable significance.

Insight from the statistical measurements suggests that the MS algorithm has a similar computational efficiency at high $T$ and even better at lower $T$'s. The MS algorithm is able to achieve  better efficiency by sampling a wider region of both conformational and sequence space. Sampling the sequence space in addition to conformational space ensures a decorrelated ensemble of states is generated.

>>>>

As a way to assess sampling efficiency, we compare in Figure~4 the statistical error, $\sigE$, of the average energy $\left <E\right >$ for the 4 different sequences obtained using ST and MS, respectively. Since roughly the same number of sampled conformations were obtained for each $\sbar$ and $T$ combination, we compare the statistical errors directly. The two algorithms give similar errors at the highest $T$ studied which implies consistent result between them. It should be noted that the highest $T$ studied is well above the folding temperature for all the 4 sequences. Therefore, this consistency is not particularly surprising since at high-T the free-energy landscape is relatively smooth. Hence, conformational space requires little difficulty to sample.

However, as temperature decreases, the statistical error from the MS algorithm generally becomes smaller than those from ST. In particular, Fig.~4C illustrates that MS is on average twice as accurate as ST in its error estimates for R1. The best estimate occurs at $\kb\approx$ 0.46 where MS is about 450\% better than ST. Even at the lowest T studied, MS is at least consistent or better than ST for all 4 sequences.
